A Sample {\ttlit Proceedings of the VLDB Endowment} Paper in LaTeX Format\titlenote{for use with vldb.cls}

### 2018-03-07 paper/paper.tex
intro checked in

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM, as well as PVLDB, seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM / PVLDB has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (2.54cm [1"] top and
bottom and 1.9cm [.75"] left and right; specified column width
(8.45cm [3.33"]) and gutter size (.083cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

@@

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.
\section{Problem}
The problem we are dealing with is the fuzzy join problem. EXPAND
\section{Algorithm}
We started our process with a simple rule based method for matching and another one for blocking. We then replaced individual peices with a machine learning method and compared the preformance. In the final product we have an elegant completly machine learning based method.
\begin{table}
\centering
\caption{Table 1}
\begin{tabular}{|c|c|} \hline
Name&Match\\ \hline
Douglas Adams&Douglas Noel Adams\\ \hline
Andreas Capellanus&Andrea Cappellano \\ \hline
John Adams Whipple&John A. Whipple \\
\hline\end{tabular}
\end{table}

\begin{table*}
\centering
\caption{Table 2}
\begin{tabular}{|c|c|} \hline
Bucket Name&Contents\\ \hline
A&\{John A. Whipple\} \\ \hline
Adams&\{Douglas Adams, Douglas Noel Adams, John Adams Whipple\} \\ \hline
Andreas&\{Andreas Capellanus\} \\ \hline
Andrea&\{Andrea Cappellano\} \\ \hline
Cappellano&\{Andrea Cappellano\} \\ \hline
Capellanus&\{Andreas Capellanus\} \\ \hline
Douglas&\{Douglas Adams, Douglas Noel Adams\} \\ \hline
John&\{John Adams Whipple, John A. Whipple\} \\ \hline
Noel&\{Douglas Noel Adams\} \\ \hline
Whipple&\{John Adams Whipple, John A. Whipple\} \\ \hline
\hline\end{tabular}
\end{table*}

In the rule-based method we block based on items that have one word in common. This is the simplest reasonable blocking strategy. In table 2 we see a what the blocking of the three names from table 1 would look like. Out of NUMBER1 pairs NUMBER2 ended up in the same bucket as all their correct matches. NUMBER3 had at least one correct match in the same bucket. To preform the actuall matching we used three simple rules. One, if two items share a word that only those two have in common match them. Two, if the we remove spaces and one of the items is a substring of the other match them. Three, if we treat each word as a member of a set representing the entity, and one set is a subset of the other we match them. We found that most of the problem with this method was not enough positives, so we accepted if any of the rules matched the two items. If we treat it as a success if the correct match is any of the top 3 we get an fscore of FSCORE1. Since the issue is mostly false-negitives, even if we accept any of the top 1000 as a success, we get FSCORE2, not much better.

The first part we replaced was the matcher. To compare the two matchers we created a rule-based matcher using the rules from the rule-based system. To replace it we created a siamese network (figure 1) INSERT FIGURE 1. A Siamese network is two deep neural networks that share weights. One entity is fed into each of the two networks. The output of the two networks is fed into a final layer which determines the distance between the two outputs and accepts or rejects. Siamese networks have been shown to work well for image matching.\footnote{CITE} Before feeding the entities into the networks, we used Kazuma charecter embeddings to encode each entity as a vector. We trained the network on our NUMBER1*0.95 pairs and withheld NUMBER1*0.05 for testing. We chose an equal number of negitive pairs to train the model on. We chose negitive pairs that had at least one word in common with the positive ones. We found that the fscore on the training data was FSCORE3 and FSCORE4 on the test date. This was better than the rule-based matcher which had an f-score of FSCORE5.

We next approached the blocking problem with machine learning. Since the hidden layer of the siamese network is optimized for matching, it should output an embedding of the entity which has its essential qualities with regaurds to matching (figure 2). We then used an aproximate nearest neighbors algorithm to find the nearest neighbors. EXPLAIN MORE Using these techniques we can find the most similar items without needing to block at all. The problem we ran into is only PERCENT1 of the correct matches were in the 10 nearest neighbors. The problem seems to be that since we trained the model using negative pairs that have at least one word in common, it did not learn that names that are completly different should be mapped seperatly (figure 3). We could try to fix this by feeding the model better negative pairs, but we found a more elegant solution. Instead of trying to aproximate the correct location using a siamese network trained for matching, we can use a triplet loss function and teach it to maximize the distance to the closest false pair and minimize the distance to the true matches. To find these closest entities we use our charecter embedings. This allowed us to get an f-score of FSCORE6 on the training set and FSCORE7 on the test set reading the 10 closest entities. Notice that at this point we can do away with the matching algorithm alltogether. We simply use the closest entiies as our matches.
\section{Related Works}
There have been a number of attemts to solve the fuzzy join problem. Many of the attemts use varios string matching algorithms for example [Fast-Join: An Efficient Method for Fuzzy TokenMatching based String Similarity Join]. The main issue with using string matching comparisons is that they do not work across a wide variaty of enties ASK DR. SRINIVAS. To our knowledge no serios machine learning aproach has been used for this problem. The problem of blocking has also been dealt with using MapReduce [Efficient Parallel Set-Similarity Joins Using MapReduce]. This approach requires alot of computing power and, since they use a string matching approach in the end, is hard to generalize accross many types of entities.

@@

% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{vldb_sample}  % vldb_sample.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references

>>>>

\include{introduction}

@@

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.
\section{Problem}
The problem we are dealing with is the fuzzy join problem. EXPAND
\section{Algorithm}
We started our process with a simple rule based method for matching and another one for blocking. We then replaced individual peices with a machine learning method and compared the preformance. In the final product we have an elegant completly machine learning based method.

\subsection{Rule-based Matching}
\begin{table}
\centering
\caption{Table 1}
\begin{tabular}{|c|c|} \hline
Name&Match\\ \hline
Douglas Adams&Douglas Noel Adams\\ \hline
Andreas Capellanus&Andrea Cappellano \\ \hline
John Adams Whipple&John A. Whipple \\
\hline\end{tabular}
\end{table}

\begin{table*}
\centering
\caption{Table 2}
\begin{tabular}{|c|c|} \hline
Bucket Name&Contents\\ \hline
A&\{John A. Whipple\} \\ \hline
Adams&\{Douglas Adams, Douglas Noel Adams, John Adams Whipple\} \\ \hline
Andreas&\{Andreas Capellanus\} \\ \hline
Andrea&\{Andrea Cappellano\} \\ \hline
Cappellano&\{Andrea Cappellano\} \\ \hline
Capellanus&\{Andreas Capellanus\} \\ \hline
Douglas&\{Douglas Adams, Douglas Noel Adams\} \\ \hline
John&\{John Adams Whipple, John A. Whipple\} \\ \hline
Noel&\{Douglas Noel Adams\} \\ \hline
Whipple&\{John Adams Whipple, John A. Whipple\} \\
\hline\end{tabular}
\end{table*}

In the rule-based method, we block based on items that have one word in common. This is the simplest reasonable blocking strategy. Table 2 illustrates what the blocking of the three names from Table 1 would look like. Out of NUMBER1 pairs, NUMBER2 ended up in the same bucket as all their correct matches. NUMBER3 had at least one correct match in the same bucket. To perform the actual matching, we used three simple rules see Table 3:
\begin{enumerate}

\item If a word is unique to two items, we match them. (`John Adams Whipple' matches `John A. Whipple' since `Whipple' only apears in those two names)
\item If, when all spaces are removed, one of the items is a substring of the other, we match them. (`the flower company' matches `theflowercompany.com' since `theflowercompany' is a subset of `theflowercompany.com')
\item If we treat each name as a set of words, and one set is a subset of the other set, we match them. (`Douglas Adams' matches `Douglas Noel Adams' since \{`Douglas', `Adams'\} $\subseteq$ \{`Douglas', `Noel', `Adams'\})

\end{enumerate} 
Even using these three rules in combination resulted in too many false negatives. Therefore we decided to treat all matches resulting from any of the three rules as valid. If we treat it as a success if there is a correct match in any of the first three slots, we get an F\textsubscript{1} of FSCORE1. Since the issue is mostly false negatives, and therefore even some of the first three slots were often empty, so even if we accept any of the top 1000 as a success, we get FSCORE2, not much better.
\subsection{Siamese Netwok}
The first part we replaced was the matcher. To compare the two matchers we created a rule-based matcher using the rules from the rule-based system. To replace it we created a siamese network (figure 1) INSERT FIGURE 1. A Siamese network is two deep neural networks that share weights. One entity is fed into each of the two networks. The output of the two networks is fed into a final layer which determines the distance between the two outputs and accepts or rejects. Siamese networks have been shown to work well for image matching.\cite{Hasdell:Siamese} Before feeding the entities into the networks, we used Kazuma charecter embeddings to encode each entity as a vector. We trained the network on our NUMBER1*0.95 pairs and withheld NUMBER1*0.05 for testing. We chose an equal number of negitive pairs to train the model on. We chose negitive pairs that had at least one word in common with the positive ones. We found that the fscore on the training data was FSCORE3 and FSCORE4 on the test date. This was better than the rule-based matcher which had an f-score of FSCORE5.

We next approached the blocking problem with machine learning. Since the hidden layer of the siamese network is optimized for matching, it should output an embedding of the entity which has its essential qualities with regaurds to matching (figure 2). We then used an aproximate nearest neighbors algorithm to find the nearest neighbors. EXPLAIN MORE Using these techniques we can find the most similar items without needing to block at all. The problem we ran into is only PERCENT1 of the correct matches were in the 10 nearest neighbors. The problem seems to be that since we trained the model using negative pairs that have at least one word in common, it did not learn that names that are completly different should be mapped seperatly (figure 3). We could try to fix this by feeding the model better negative pairs, but we found a more elegant solution. Instead of trying to aproximate the correct location using a siamese network trained for matching, we can use a triplet loss function and teach it to maximize the distance to the closest false pair and minimize the distance to the true matches. To find these closest entities we use our charecter embedings. This allowed us to get an f-score of FSCORE6 on the training set and FSCORE7 on the test set reading the 10 closest entities. Notice that at this point we can do away with the matching algorithm alltogether. We simply use the closest entiies as our matches.
\section{Related Works}
There have been a number of attemts to solve the fuzzy join problem. Many of the attemts use varios string matching algorithms for example \cite{Wang:String}. The main issue with using string matching comparisons is that they do not work across a wide variaty of enties ASK DR. SRINIVAS. To our knowledge no serios machine learning aproach has been used for this problem. The problem of blocking has also been dealt with using MapReduce \cite{Vernica:MapReduce}. This approach requires alot of computing power and, since they use a string matching approach in the end, is hard to generalize accross many types of entities.

@@

% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}  % vldb_sample.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
